The Astropy Project

### 2017-12-14 author.tex
first draft of the author list

\author[0000-0002-3713-6337]{B. M. Sip\H{o}cz}
\affil{TBD}

@@

\author[0000-0002-4576-9337]{M. Bachetti}
\affil{INAF-Osservatorio Astronomico di Cagliari}

\author{A. V. Bakanov}
\affil{}

@@

\author{K. L. Berry}
\affil{}

@@

\author{E. M. Bray}
\affil{}

@@

\author{T. Finethy}
\affil{}

\author[0000-0003-4291-1091]{R. T. Fox}
\affil{Unaffiliated}

@@

\author[0000-0001-6431-9633]{A. Ginsburg}
\affil{National Radio Astronomy Observatory, 1003 Lopezville Road Socorro, NM 87801-0387}

@@

\author{F. Grollier}
\affil{Independent developer}

@@

\author{A. Khvalko}
\affil{}

@@

\author[0000-0002-1395-8694]{D. M. Macleod}
\affil{}

\author[0000-0002-6324-5713]{M. Mastropietro}
\affil{Ghent University}

@@

\author{S. Montagnac}
\affil{obs-psr}

\author[0000-0003-2528-3409]{B. M. Morris}
\affil{University of Washington}

@@

\author{M. N{\"o}the}
\affil{TU Dortmund, Germany}

@@

\author[0000-0001-7790-5308]{S. Oh}
\affil{Princeton University}

@@

\author[0000-0002-9351-6051]{S. Pascual}
\affil{Universidad Complutense de Madrid}

\author{R. Patil}
\affil{}

@@

\author{T. Rastogi}
\affil{}

@@

\author{M. Seifert}
\affil{}

@@

\author[0000-0003-0477-6220]{H. Sherwood-Taylor}
\affil{}

@@

\author{M. T. Silbiger}
\affil{}

@@

\author{K. A. Sooley}
\affil{}

\author{S. Sornarajah}
\affil{}

@@

\author[0000-0003-1774-3436]{P. Teuben}
\affil{University of Maryland}

@@

\author[0000-0003-2638-7648]{V. Zabalza}
\affil{}

>>>>

\author[0000-0002-3713-6337]{B. M. Sip\H{o}cz}
%\affil{}

@@

\author[0000-0002-4576-9337]{M. Bachetti}
\affil{INAF-Osservatorio Astronomico di Cagliari, via della Scienza 5, I-09047, Selargius, Italy}

\author{A. V. Bakanov}
%\affil{}

@@

\author{K. L. Berry}
%\affil{}

@@

\author{E. M. Bray}
%\affil{}

@@

\author{T. Finethy}
%\affil{}

\author[0000-0003-4291-1091]{R. T. Fox}
%\affil{}

@@

@@

\author{F. Grollier}
%\affil{}

@@

\author{A. Khvalko}
%\affil{}

@@

\author[0000-0002-1395-8694]{D. M. Macleod}
%\affil{}

\author[0000-0002-6324-5713]{M. Mastropietro}
\affil{Department Physics and Astronomy, Ghent University, Krijgslaan 281, S9, B-9000 Gent, Belgium}

@@

\author{S. Montagnac}
\affil{Puy-Sainte-R\'eparade Observatory}

\author[0000-0003-2528-3409]{B. M. Morris}
\affil{Astronomy Department, University of Washington, Seattle, WA 98195, USA}

@@

\author{M. N{\"o}the}
\affil{TU Dortmund, Experimental Physics 5, Otto-Hahn-Str. 4, 44221 Dortmund, Germany}

@@

\author[0000-0001-7790-5308]{S. Oh}
\affil{Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08544, USA}

@@

\author[0000-0002-9351-6051]{S. Pascual}
\affil{Departamento de Astrofisica, Universidad Complutense de Madrid, Madrid, Spain}

\author{R. Patil}
%\affil{}

@@

\author{T. Rastogi}
%\affil{}

@@

\author{M. Seifert}
%\affil{}

@@

\author[0000-0003-0477-6220]{H. Sherwood-Taylor}
%\affil{}

@@

\author{M. T. Silbiger}
%\affil{}

@@

\author{K. A. Sooley}
%\affil{}

\author{S. Sornarajah}
%\affil{}

@@

\author[0000-0003-1774-3436]{P. Teuben}
\affil{Astronomy Department, University of Maryland, College Park, MD. 20742, USA}

@@

\author[0000-0003-2638-7648]{V. Zabalza}
%\affil{}

### 2017-12-14 main.tex
first draft of the author list

\author{Astropy Project}
\footnote{The author list has three parts: the 13 authors that were primary authors of  sections of the paper in order of contribution, the four members of the \astropy Project coordination committee, and contributions to the \astropy Project in alphabetical order.  The position in the author list does not correspond to contributions to the \astropy Project as a whole.  A more complete list of contributors to the core package can be found in the \href{https://github.com/astropy/astropy/graphs/contributors}{package repository}, and at the \href{http://www.astropy.org/team.html}{\astropy team webpage}.}

@@

\acknowledgments The \astropy community is supported by and makes use
of a number of organizations and services outside the traditional
academic community. We thank Google for financing and organizing the
Google Summer of Code (GSoC) program, that has funded severals
students per year to work on \astropy related projects over the
summer. These students often turn into long-term contributors. We also
thank NumFOCUS and the Python Software Foundation for financial
support. Within the academic community, we thank
institutions that make it possible that astronomers and other developers on
their staff can contribute their time to the development of
\astropy projects.

>>>>

\author{Astropy Project}
\footnote{The author list has three parts: the 13 authors that made significant contributions to the  writing of the paper in order of contribution, the four members of the \astropy Project coordination committee, and contributions to the \astropy Project in alphabetical order.  The position in the author list does not correspond to contributions to the \astropy Project as a whole.  A more complete list of contributors to the core package can be found in the \href{https://github.com/astropy/astropy/graphs/contributors}{package repository}, and at the \href{http://www.astropy.org/team.html}{\astropy team webpage}.}

@@

\acknowledgments

The \astropy community is supported by and makes use
of a number of organizations and services outside the traditional
academic community. We thank Google for financing and organizing the
Google Summer of Code (GSoC) program, that has funded severals
students per year to work on \astropy related projects over the
summer. These students often turn into long-term contributors. We also
thank NumFOCUS and the Python Software Foundation for financial
support. Within the academic community, we thank
institutions that make it possible that astronomers and other developers on
their staff can contribute their time to the development of
\astropy projects.
